Testing Statistical Graphics

### 2022-06-29 index.qmd
A real abstract

abstract: |
  We outline our process and common pitfalls for developing and testing human perception of statistical graphics. 
  Goal: Integrate information from the design of \cite{clusters,sineillusion,emily-diss,power}.

>>>>

abstract: |
  In this paper, we discuss considerations and methods for experimentally testing visualizations. We discuss levels of user engagement with graphics, common issues when developing a sampling or data generation model, the importance of pilot testing, and data analysis methods. Along the way, we also share hard-learned lessons on what not to do and some of the unique pitfalls of human testing in statistical and visualization research.
